### 2020-06-25 cv/cv-body.tex
Update CV
Quick partial cv update

\begin{description}
\tightlist
\item[2017--present]
Program Head in Analytical Approaches and Spatial Stock Assessment,
Groundfish Section, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada\\
Associate Editor at the Canadian Journal of Fisheries and Aquatic
Sciences
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA, USA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University, Burnaby, BC, Canada
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University, Burnaby, BC, Canada
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie
University, Halifax, NS, Canada
\end{description}

@@

\begin{description}
\tightlist
\item[2020]
\textbf{Anderson, S.C.}, A.M. Edwards, M. Yerlanov, N. Mulberry, J.
Stockdale, S.A. Iyaniwura, R.C. Falcao, M.C. Otterstatter, M.A.\ Irvine,
N.Z. Janjua, D. Coombs, C. Colijn. Estimating the impact of COVID-19
control measures using a Bayesian model of physical distancing. medRxiv
2020.04.17.20070086. \url{https://doi.org/10.1101/2020.04.17.20070086}.
\end{description}

@@

\begin{description}
\tightlist
\item[2018]
One-day workshop on Bayesian data analysis for ecologists with Stan.
\url{https://github.com/seananderson/bayes-course}
\item[2018]
Two two-day workshops on advanced generalized linear mixed-effects
modeling in R for the Simon Fraser University Library Research Commons.
\url{https://github.com/seananderson/glmm-course}
\item[2017]
One-and-a-half-day workshop on linear mixed-effects modeling in R and
generalized linear modeling in R for the David H. Smith Conservation
Postdoctoral Research Fellows.
\url{https://github.com/seananderson/glmm-course}
\item[2016]
Two two-day workshops on advanced generalized linear mixed-effects
modeling in R for the Simon Fraser University Library Research Commons.
\url{https://github.com/seananderson/glmm-course}
\item[2014--16]
Developed self-directed lecture and exercises on ggplot2 for FISH 554:
Beautiful graphics in R, School of Aquatic and Fishery Sciences,
University of Washington, Seattle, WA, United States.\\
\url{http://seananderson.ca/ggplot2-FISH554/}
\item[2013--14]
Organizer of Stats Beerz --- a statistical help group attended by
graduate students and postdocs primarily in the Earth to Oceans research
group, but also the wider SFU Biology and Geography Departments, and the
School of Resource and Environmental Management (REM).
\item[2013]
Two-part workshop on data manipulation for Stats Beerz and Earth to
Oceans groups at Simon Fraser University with approximately 25
participants. An introduction to plyr, advanced concepts with plyr and
function debugging, and an introduction to dplyr.\\
\url{https://github.com/seananderson/plyr-statsbeerz}
\item[2013]
Instructor for BISC-888-1: Data Wrangling and Visualization in R, a
graduate-level course at Simon Fraser University, Burnaby, BC, Canada
with approximately 20 participants. Co-developed curriculum and
developed/delivered lectures, exercises, notes, and assignments for
three of six two-hour classes.\\
\url{https://github.com/seananderson/datawranglR} (see classes 03, 04,
05)
\item[2012]
Introduction to ggplot2.
(\href{http://seananderson.ca/courses/12-ggplot2/ggplot2_notes.pdf}{notes},
\href{http://seananderson.ca/courses/12-ggplot2/ggplot2_slides_with_examples.pdf}{slides})
Lecture for FISH 507H: Beautiful Graphics in R, School of Aquatic and
Fishery Sciences, University of Washington, Seattle, WA, United States
\item[2012]
Workshop on the R package plyr.
(\href{http://seananderson.ca/courses/12-plyr/plyr_2012.pdf}{notes},
\href{http://seananderson.ca/courses/12-plyr/plyr_2012_slides.pdf}{slides},
\href{http://seananderson.ca/courses/12-plyr/plyr_2012_examples.html}{examples})
Branch Lab, School of Aquatic and Fishery Sciences, University of
Washington, Seattle, WA, United States
\item[2011]
Multipanel plotting in R with base graphics.
(\href{http://seananderson.ca/courses/11-multipanel/multipanel.pdf}{notes},
\href{http://seananderson.ca/courses/11-multipanel/multipanel-slides.pdf}{slides}).
Earth2Ocean Research Group, Simon Fraser University, Burnaby, BC,
Canada.
\item[2011]
A brief introduction to R.
(\href{http://seananderson.ca/courses/11-rintro/RIntro.pdf}{notes},
\href{http://seananderson.ca/courses/11-rintro/RIntro.R}{workshop
code}). Earth2Ocean Research Group, Simon Fraser University, Burnaby,
BC, Canada.
\item[2011]
Workshop on the R package plyr
(\href{http://seananderson.ca/courses/11-plyr/plyr.pdf}{notes},
\href{http://seananderson.ca/courses/11-plyr/plyr-slides.pdf}{slides}).
Earth2Ocean Research Group, Simon Fraser University, Burnaby, BC,
Canada.
\item[2007--08]
Teaching Assistant, Organismal Biology and Ecology, Dalhousie
University, two semesters (BIOL 1021).
\item[2007--08]
Teaching Assistant, Marine Mammology, Dalhousie University (BIOL 4060).
\end{description}

>>>>

\begin{description}
\tightlist
\item[2017--present]
Program Head in Analytical Approaches and Spatial Stock Assessment,
Groundfish Section, Stock Assessment and Research Division, Pacific
Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, Canada
\end{description}

2020--present Adjunct Professor, Department of Mathematics, Simon Fraser
University

2019--present Associate Editor, the Canadian Journal of Fisheries and
Aquatic Sciences

\begin{description}
\tightlist
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie University
\end{description}

@@

\begin{description}
\tightlist
\item[2020]
\textbf{Anderson, S.C.}, Mulberry, N., Edwards, A.M., Stockdale, J.E.,
Iyaniwura, S.A., Falcao, R.C., Otterstatter, M.C., Janjua, N.Z., Coombs,
D., and Colijn, C. 2020. How much leeway is there to relax COVID-19
control measures? medRxiv 2020.06.12.20129833.
\url{https://doi.org/10.1101/2020.06.12.20129833}.
\item[2020]
\textbf{Anderson, S.C.}, A.M. Edwards, M. Yerlanov, N. Mulberry, J.
Stockdale, S.A. Iyaniwura, R.C. Falcao, M.C. Otterstatter, M.A.\ Irvine,
N.Z. Janjua, D. Coombs, C. Colijn. Estimating the impact of COVID-19
control measures using a Bayesian model of physical distancing. medRxiv
2020.04.17.20070086. \url{https://doi.org/10.1101/2020.04.17.20070086}.
\end{description}

@@

Two-day workshop on Advanced R topics (functional programming,
debugging, profiling, benchmarking, parallel processing, integrating C++
with R). University of British Columbia.
\url{https://github.com/seananderson/adv-r-course}
One-day workshop on Bayesian data analysis for ecologists with Stan for
the David H. Smith Conservation Research Fellowship Program.
\url{https://github.com/seananderson/bayes-course}
Two two-day workshops on advanced generalized linear mixed-effects
modeling in R for the Simon Fraser University Library Research Commons.
\url{https://github.com/seananderson/glmm-course}
One-and-a-half-day workshop on linear mixed-effects modeling in R and
generalized linear modeling in R for the David H. Smith Conservation
Postdoctoral Research Fellows.
\url{https://github.com/seananderson/glmm-course}
Two two-day workshops on advanced generalized linear mixed-effects
modeling in R for the Simon Fraser University Library Research Commons.
\url{https://github.com/seananderson/glmm-course}
\item[2014--16]
Developed self-directed lecture and exercises on ggplot2 for FISH 554:
Beautiful graphics in R, School of Aquatic and Fishery Sciences,
University of Washington, Seattle, WA, United States.\\
\url{http://seananderson.ca/ggplot2-FISH554/}
\item[2013--14]
Organizer of Stats Beerz --- a statistical help group attended by
graduate students and postdocs primarily in the Earth to Oceans research
group, but also the wider SFU Biology and Geography Departments, and the
School of Resource and Environmental Management (REM).
Two-part workshop on data manipulation for Stats Beerz and Earth to
Oceans groups at Simon Fraser University with approximately 25
participants. An introduction to plyr, advanced concepts with plyr and
function debugging, and an introduction to dplyr.\\
\url{https://github.com/seananderson/plyr-statsbeerz}
Instructor for BISC-888-1: Data Wrangling and Visualization in R, a
graduate-level course at Simon Fraser University, Burnaby, BC, Canada
with approximately 20 participants. Co-developed curriculum and
developed/delivered lectures, exercises, notes, and assignments for
three of six two-hour classes.\\
\url{https://github.com/seananderson/datawranglR} (see classes 03, 04,
05)
Introduction to ggplot2.
(\href{http://seananderson.ca/courses/12-ggplot2/ggplot2_notes.pdf}{notes},
\href{http://seananderson.ca/courses/12-ggplot2/ggplot2_slides_with_examples.pdf}{slides})
Lecture for FISH 507H: Beautiful Graphics in R, School of Aquatic and
Fishery Sciences, University of Washington, Seattle, WA, United States
Workshop on the R package plyr.
(\href{http://seananderson.ca/courses/12-plyr/plyr_2012.pdf}{notes},
\href{http://seananderson.ca/courses/12-plyr/plyr_2012_slides.pdf}{slides},
\href{http://seananderson.ca/courses/12-plyr/plyr_2012_examples.html}{examples})
Branch Lab, School of Aquatic and Fishery Sciences, University of
Washington, Seattle, WA, United States
Multipanel plotting in R with base graphics.
(\href{http://seananderson.ca/courses/11-multipanel/multipanel.pdf}{notes},
\href{http://seananderson.ca/courses/11-multipanel/multipanel-slides.pdf}{slides}).
Earth2Ocean Research Group, Simon Fraser University, Burnaby, BC,
Canada.
A brief introduction to R.
(\href{http://seananderson.ca/courses/11-rintro/RIntro.pdf}{notes},
\href{http://seananderson.ca/courses/11-rintro/RIntro.R}{workshop
code}). Earth2Ocean Research Group, Simon Fraser University, Burnaby,
BC, Canada.
Workshop on the R package plyr
(\href{http://seananderson.ca/courses/11-plyr/plyr.pdf}{notes},
\href{http://seananderson.ca/courses/11-plyr/plyr-slides.pdf}{slides}).
Earth2Ocean Research Group, Simon Fraser University, Burnaby, BC,
Canada.
\item[2007--08]
Teaching Assistant, Organismal Biology and Ecology, Dalhousie
University, two semesters (BIOL 1021).
\item[2007--08]
Teaching Assistant, Marine Mammology, Dalhousie University (BIOL 4060).
